Translation Elicitation

### 2021-05-21 Rmd/report.Rmd
Fix model

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = TRUE,
  warning = TRUE, 
  cache.extra = knitr::rand_seed,
  out.width = "100%",
  results = "asis",
  dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-')
```

@@

# load packages
library(tidyverse)
library(gt)
library(lubridate)
library(ggdist)
library(readxl)
library(tidytext)
library(brms)
library(tidybayes)
library(patchwork)
library(mice)
library(here)

@@

# import data
trials <- readRDS(here("Data", "trials.rds"))
participants <- readRDS(here("Data", "participants.rds"))
responses <- readRDS(here("Data", "accuracy.rds"))
jtrace <- readRDS(here("Data", "jtrace.rds"))

# import models
fit_jtrace <- readRDS(here("Results", "fit_jtrace.rds"))
fit_responses <- readRDS(here("Results", "fit.rds"))
fit_responses_coefs <- readRDS(here("Results", "coefficients.rds")) %>% 
  select(term, estimate, std.error, conf.low, conf.high)

@@

# Experimental task: Translation Elicitation

@@

We collected data from `r format(as_date(min(participants$date)), "%B %dth %Y")` to `r format(as_date(max(participants$date)), "%B %dth %Y")`. We tested `r length(unique(participants$participant))` participants. `r length(unique(participants$participant[participants$group=="ENG-SPA"]))` were English natives tested in Spanish, `r length(unique(participants$participant[participants$group=="ENG-CAT"]))` were English natives tested in Catalan, and `r length(unique(participants$participant[participants$group=="SPA-CAT"]))` were Spanish natives tested in Catalan. `r sum(!participants$valid_participant)` failed to meet all the inclusion criteria and were excluded from further analyses.

@@

@@

#### Stress position

```{r trials_stress, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
trials_coded %>% 
  select(trial_id, group, overlap_stress) %>% 
  ggplot(aes(group, fill = overlap_stress, colour = overlap_stress)) +
  geom_bar(position = position_dodge(width = 0.9)) +
  labs(x = "Group", y = "# trials", fill = "Same stress position?", colour = "Same stress position?") +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

### Data analysis

ggplot(responses_item, aes(reorder(word_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5, colour = "red") +
  geom_errorbar() +
  geom_point(size = 0.5) +
  labs(y = "Correct responses", x = "Word", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  )

ggplot(responses_participant, aes(reorder(participant_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5, colour = "red") +
  geom_errorbar(width = 0.5) +
  geom_point(size = 1) +
  labs(y = "Correct responses", x = "Participant", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  )

### Bayesian regression model {.tabset .tab-pill}

@@

* PTHN (`pthn`, 0-Inf): number of phonological neighbours with higher frequency of the target word. Extracted from the CLEARPOND database.
* Lexical frequency (`frequency`, 0-Inf): lexical frequency (counts per million) of the target word. Extracted from the SUBTLEX database (via CLEAPOND).
* Vowel similarity (`vowel_ratio`, 0-1): edit distance between the sequence of vowels of the presented word  and the target word. Computed using custom code.
* Consonant similarity (`consonant_ratio`, 0-1): edit distance between the sequence of consonants of the presented word and the target word. Computed using custom code.
* Shared phonological onset (`onset`, 0 or 1): do the presented word and the target word share phonological onset? Manually coded.
* Share stress position (`overlap_stress`, 0 or 1): are the presented word and the target word stressed at the same position? Manually coded.

@@

```{stan stan_model, echo=TRUE, output.var="model"}
// generated with brms 2.15.0
functions {
 /* compute correlated group-level effects
  * Args: 
  *   z: matrix of unscaled group-level effects
  *   SD: vector of standard deviation parameters
  *   L: cholesky factor correlation matrix
  * Returns: 
  *   matrix of scaled group-level effects
  */ 
  matrix scale_r_cor(matrix z, vector SD, matrix L) {
    // r is stored in another dimension order than z
    return transpose(diag_pre_multiply(SD, L) * z);
  }
}
data {
  int<lower=1> N;  // total number of observations
  int Y[N];  // response variable
  int<lower=1> K;  // number of population-level effects
  matrix[N, K] X;  // population-level design matrix
  // data for group-level effects of ID 1
  int<lower=1> N_1;  // number of grouping levels
  int<lower=1> M_1;  // number of coefficients per level
  int<lower=1> J_1[N];  // grouping indicator per observation
  // group-level predictor values
  vector[N] Z_1_1;
  vector[N] Z_1_2;
  vector[N] Z_1_3;
  vector[N] Z_1_4;
  vector[N] Z_1_5;
  vector[N] Z_1_6;
  vector[N] Z_1_7;
  int<lower=1> NC_1;  // number of group-level correlations
  // data for group-level effects of ID 2
  int<lower=1> N_2;  // number of grouping levels
  int<lower=1> M_2;  // number of coefficients per level
  int<lower=1> J_2[N];  // grouping indicator per observation
  // group-level predictor values
  vector[N] Z_2_1;
  int prior_only;  // should the likelihood be ignored?
}
transformed data {
  int Kc = K - 1;
  matrix[N, Kc] Xc;  // centered version of X without an intercept
  vector[Kc] means_X;  // column means of X before centering
  for (i in 2:K) {
    means_X[i - 1] = mean(X[, i]);
    Xc[, i - 1] = X[, i] - means_X[i - 1];
  }
}
parameters {
  vector[Kc] b;  // population-level effects
  real Intercept;  // temporary intercept for centered predictors
  matrix[M_1, N_1] z_1;  // standardized group-level effects
  cholesky_factor_corr[M_1] L_1;  // cholesky factor of correlation matrix
  vector<lower=0>[M_2] sd_2;  // group-level standard deviations
  vector[N_2] z_2[M_2];  // standardized group-level effects
}
transformed parameters {
  vector<lower=0>[M_1] sd_1;  // group-level standard deviations
  matrix[N_1, M_1] r_1;  // actual group-level effects
  // using vectors speeds up indexing in loops
  vector[N_1] r_1_1;
  vector[N_1] r_1_2;
  vector[N_1] r_1_3;
  vector[N_1] r_1_4;
  vector[N_1] r_1_5;
  vector[N_1] r_1_6;
  vector[N_1] r_1_7;
  vector[N_2] r_2_1;  // actual group-level effects
  sd_1 = rep_vector(1, rows(sd_1));
  // compute actual group-level effects
  r_1 = scale_r_cor(z_1, sd_1, L_1);
  r_1_1 = r_1[, 1];
  r_1_2 = r_1[, 2];
  r_1_3 = r_1[, 3];
  r_1_4 = r_1[, 4];
  r_1_5 = r_1[, 5];
  r_1_6 = r_1[, 6];
  r_1_7 = r_1[, 7];
  r_2_1 = (sd_2[1] * (z_2[1]));
}
model {
  // likelihood including constants
  if (!prior_only) {
    // initialize linear predictor term
    vector[N] mu = Intercept + rep_vector(0.0, N);
    for (n in 1:N) {
      // add more terms to the linear predictor
      mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_1_2[J_1[n]] * Z_1_2[n] + r_1_3[J_1[n]] * Z_1_3[n] + r_1_4[J_1[n]] * Z_1_4[n] + r_1_5[J_1[n]] * Z_1_5[n] + r_1_6[J_1[n]] * Z_1_6[n] + r_1_7[J_1[n]] * Z_1_7[n] + r_2_1[J_2[n]] * Z_2_1[n];
    }
    target += bernoulli_logit_glm_lpmf(Y | Xc, mu, b);
  }
  // priors including constants
  target += normal_lpdf(b | 0, 1);
  target += normal_lpdf(Intercept | 0, 1);
  target += std_normal_lpdf(to_vector(z_1));
  target += lkj_corr_cholesky_lpdf(L_1 | 5);
  target += cauchy_lpdf(sd_2 | 0, 3)
    - 1 * cauchy_lccdf(0 | 0, 3);
  target += std_normal_lpdf(z_2[1]);
}
generated quantities {
  // actual population-level intercept
  real b_Intercept = Intercept - dot_product(means_X, b);
  // compute group-level correlations
  corr_matrix[M_1] Cor_1 = multiply_lower_tri_self_transpose(L_1);
  vector<lower=-1,upper=1>[NC_1] cor_1;
  // extract upper diagonal of correlation matrix
  for (k in 1:M_1) {
    for (j in 1:(k - 1)) {
      cor_1[choose(k - 1, 2) + j] = Cor_1[j, k];
    }
  }
}

@@

@@

```{r coefs_fixed_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(fit_responses)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercep)", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="(Intercept)")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("pthn", "frequency", "consonant_ratio", "vowel_ratio", "onset1", "overlap_stress1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  )
```

@@

ggplot(post, aes(.value, fill = .variable)) +
  facet_wrap(~.variable, scales = "free") +
  geom_vline(xintercept = 0, colour = "red") +
  stat_halfeye() +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

ggplot(post_re, aes(.value, sort(as.factor(participant)), xmin = .lower, xmax = .upper, colour = group)) +
  facet_grid(group~.param, scales = "free_y") +
  geom_errorbarh(height = 0.5, alpha = 0.75) +
  geom_point(size = 0.1, shape = 4) +
  geom_vline(xintercept = 0, colour = "red") +
  labs(x = "Participant-level adjustment", y = "Participant", colour = "Group") +
  theme_custom() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    axis.text.x = element_text(size = 9),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

#### Marginal effects

```{r emmeans, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
nd <- expand_grid(
  pthn = seq(
    min(responses_coded$pthn, na.rm = TRUE),
    max(responses_coded$pthn, na.rm = TRUE),
    by = 0.1
  ),
  onset = unique(responses_coded$onset),
  overlap_stress = unique(responses_coded$overlap_stress),
  vowel_ratio = c(-1, 1),
  consonant_ratio = c(-1, 1)
) %>% 
  mutate(frequency = 0)

m <- add_fitted_draws(nd, fit_responses, n = 20, re_formula = NA) %>% 
  mutate_at(vars(ends_with("_ratio")),
            function(x) ifelse(x>0, paste0(x, " SD"), paste0("-", x, " SD")))

ggplot(m, aes(pthn, .value, 
              colour = interaction(consonant_ratio, vowel_ratio, sep = "/"),
              fill = interaction(consonant_ratio, vowel_ratio, sep = "/"))) +
  facet_grid(~overlap_stress~onset) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Phonological neighbourhood density\n(higher frequency neighbours)",
       y = "P(Correct)", colour = "Consonant/Vowel similarity",
       fill = "Consonant similarity / Vowel similarity") +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

```{r jtrace_all_plot, echo=FALSE, warning=FALSE}
ggplot(jtrace, aes(x = activation, y = pct_participant)) +
  geom_smooth() +
  geom_point(shape = 1, stroke = 1, alpha = 0.5) +
  labs(
    x = "jTRACE activation value for the word",
    y = "% participants who responded with the word",
    title = "jTRACE activation against % participants who gave word as response"
  ) +
  theme_custom() +
  theme(
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

# plot by word
jtrace %>% 
  mutate(input_language = paste0(input, " (", language, ")")) %>% 
  ggplot(aes(x = activation, y = pct_participant)) +
  facet_wrap(~input_language) +
  geom_smooth() +
  geom_point(shape = 1, stroke = 1, alpha = 0.5) +
  labs(
    x = "jTRACE activation value for the word",
    y = "% participants who responded with the word",
    title = "jTRACE activation against % participants who gave word as response"
  ) +
  theme_custom() +
  theme(
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = TRUE,
  warning = TRUE, 
  cache.extra = knitr::rand_seed,
  out.width = "100%",
  results = "asis",
  dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
        ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.continuous.fill = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.continuous.colour = wesanderson::wes_palettes$Darjeeling1
)

@@

# load packages
library(tidyverse)
library(gt)
library(lubridate)
library(wesanderson)
library(ggdist)
library(readxl)
library(tidytext)
library(brms)
library(tidybayes)
library(patchwork)
library(mice)
library(here)

@@

# import data
trials <- readRDS(here("Data", "trials.rds"))
participants <- readRDS(here("Data", "participants.rds"))
responses <- readRDS(here("Data", "responses.rds"))
jtrace <- readRDS(here("Data", "jtrace.rds"))

# import models
fit_jtrace <- readRDS(here("Results", "fit_jtrace.rds"))
fit_responses <- readRDS(here("Results", "fit_responses.rds"))

@@

# Experimental task

@@

We collected data from `r format(as_date(min(participants$date)), "%B %dth %Y")` to `r format(as_date(max(participants$date)), "%B %dth %Y")`. We tested `r length(unique(participants$participant))` participants. `r length(unique(participants$participant[participants$group=="ENG-SPA"]))` were English natives tested in Spanish, `r length(unique(participants$participant[participants$group=="ENG-CAT"]))` were English natives tested in Catalan, and `r length(unique(participants$participant[participants$group=="SPA-CAT"]))` were Spanish natives tested in Catalan. `r sum(!participants$valid_participant)` failed to meet all the inclusion criteria and were excluded from further analyses. The final sample comprised data from `r sum(!participants$valid_participant)` participants, `r sum(participants$valid_participant[participants$group=="ENG-SPA"])` in the ENG-SPA group, `r sum(participants$valid_participant[participants$group=="ENG-CAT"])` in the ENG-CAT group, and `r sum(participants$valid_participant[participants$group=="SPA-CAT"])` in the SPA-CAT group.

@@

Participants in the ENG-SPA listened to `r nrow(trials[trials$group=="ENG-SPA",])` Spanish words, and participants in the ENG-CAT and the SPA-CAT groups listened to `nrow(trials[trials$group=="ENG-CAT",]) trials`. Five trials in each condition were practice trials and were excluded from analyses.

@@

@@

### Data analysis {.tabset .tab-pills}

@@

* PTHN (`pthn`, 0-Inf): number of phonological neighbours with higher frequency of the target word. Extracted from the CLEARPOND database.
* Vowel similarity (`vowel_ratio`, 0-1): edit distance between the sequence of vowels of the presented word  and the target word. Computed using custom code.
* Consonant similarity (`consonant_ratio`, 0-1): edit distance between the sequence of consonants of the presented word and the target word. Computed using custom code.
* Shared phonological onset (`onset`, 0 or 1): do the presented word and the target word share phonological onset? Manually coded.

@@

```{stan stan_model, echo=TRUE, output.var="model"}
// generated with brms 2.15.0
functions {
/* compute correlated group-level effects
* Args: 
*   z: matrix of unscaled group-level effects
*   SD: vector of standard deviation parameters
*   L: cholesky factor correlation matrix
* Returns: 
*   matrix of scaled group-level effects
*/ 
matrix scale_r_cor(matrix z, vector SD, matrix L) {
// r is stored in another dimension order than z
return transpose(diag_pre_multiply(SD, L) * z);
}
}
data {
int<lower=1> N;  // total number of observations
int Y[N];  // response variable
int<lower=1> K;  // number of population-level effects
matrix[N, K] X;  // population-level design matrix
// data for group-level effects of ID 1
int<lower=1> N_1;  // number of grouping levels
int<lower=1> M_1;  // number of coefficients per level
int<lower=1> J_1[N];  // grouping indicator per observation
// group-level predictor values
vector[N] Z_1_1;
vector[N] Z_1_2;
vector[N] Z_1_3;
vector[N] Z_1_4;
vector[N] Z_1_5;
vector[N] Z_1_6;
vector[N] Z_1_7;
int<lower=1> NC_1;  // number of group-level correlations
// data for group-level effects of ID 2
int<lower=1> N_2;  // number of grouping levels
int<lower=1> M_2;  // number of coefficients per level
int<lower=1> J_2[N];  // grouping indicator per observation
// group-level predictor values
vector[N] Z_2_1;
int prior_only;  // should the likelihood be ignored?
}
transformed data {
int Kc = K - 1;
matrix[N, Kc] Xc;  // centered version of X without an intercept
vector[Kc] means_X;  // column means of X before centering
for (i in 2:K) {
means_X[i - 1] = mean(X[, i]);
Xc[, i - 1] = X[, i] - means_X[i - 1];
}
}
parameters {
vector[Kc] b;  // population-level effects
real Intercept;  // temporary intercept for centered predictors
matrix[M_1, N_1] z_1;  // standardized group-level effects
cholesky_factor_corr[M_1] L_1;  // cholesky factor of correlation matrix
vector<lower=0>[M_2] sd_2;  // group-level standard deviations
vector[N_2] z_2[M_2];  // standardized group-level effects
}
transformed parameters {
vector<lower=0>[M_1] sd_1;  // group-level standard deviations
matrix[N_1, M_1] r_1;  // actual group-level effects
// using vectors speeds up indexing in loops
vector[N_1] r_1_1;
vector[N_1] r_1_2;
vector[N_1] r_1_3;
vector[N_1] r_1_4;
vector[N_1] r_1_5;
vector[N_1] r_1_6;
vector[N_1] r_1_7;
vector[N_2] r_2_1;  // actual group-level effects
sd_1 = rep_vector(1, rows(sd_1));
// compute actual group-level effects
r_1 = scale_r_cor(z_1, sd_1, L_1);
r_1_1 = r_1[, 1];
r_1_2 = r_1[, 2];
r_1_3 = r_1[, 3];
r_1_4 = r_1[, 4];
r_1_5 = r_1[, 5];
r_1_6 = r_1[, 6];
r_1_7 = r_1[, 7];
r_2_1 = (sd_2[1] * (z_2[1]));
}
model {
// likelihood including constants
if (!prior_only) {
// initialize linear predictor term
vector[N] mu = Intercept + rep_vector(0.0, N);
for (n in 1:N) {
// add more terms to the linear predictor
mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_1_2[J_1[n]] * Z_1_2[n] + r_1_3[J_1[n]] * Z_1_3[n] + r_1_4[J_1[n]] * Z_1_4[n] + r_1_5[J_1[n]] * Z_1_5[n] + r_1_6[J_1[n]] * Z_1_6[n] + r_1_7[J_1[n]] * Z_1_7[n] + r_2_1[J_2[n]] * Z_2_1[n];
}
target += bernoulli_logit_glm_lpmf(Y | Xc, mu, b);
}
// priors including constants
target += normal_lpdf(b | 0, 1);
target += normal_lpdf(Intercept | 0, 1);
target += std_normal_lpdf(to_vector(z_1));
target += lkj_corr_cholesky_lpdf(L_1 | 5);
target += cauchy_lpdf(sd_2 | 0, 3)
- 1 * cauchy_lccdf(0 | 0, 3);
target += std_normal_lpdf(z_2[1]);
}
generated quantities {
// actual population-level intercept
real b_Intercept = Intercept - dot_product(means_X, b);
// compute group-level correlations
corr_matrix[M_1] Cor_1 = multiply_lower_tri_self_transpose(L_1);
vector<lower=-1,upper=1>[NC_1] cor_1;
// extract upper diagonal of correlation matrix
for (k in 1:M_1) {
for (j in 1:(k - 1)) {
cor_1[choose(k - 1, 2) + j] = Cor_1[j, k];
}
}
}
```

ggplot(responses_item, aes(reorder(word_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5, colour = "black") +
  geom_errorbar() +
  geom_point(size = 0.5) +
  labs(y = "Correct responses", x = "Word", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "accuracy_item.png"))

@@

ggplot(responses_participant, aes(reorder(participant_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5) +
  geom_errorbar(width = 0.5) +
  geom_point(size = 1) +
  labs(y = "Correct responses", x = "Participant", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "accuracy_participant.png"))

### Model outputs {.tabset .tab-pill}

@@

```{r coefs_fixed_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(fit_responses)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercep)", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="(Intercept)")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("pthn", "consonant_ratio", "vowel_ratio", "onset1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  )
```

@@

ggplot(post, aes(.value, fill = .variable)) +
  facet_wrap(~.variable, scales = "free") +
  geom_vline(xintercept = 0) +
  stat_halfeye() +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_fixed.png"))
```

@@

ggplot(post_re, aes(.value, sort(as.factor(participant)), xmin = .lower, xmax = .upper, colour = group)) +
  facet_grid(group~.param, scales = "free_y") +
  geom_errorbarh(height = 0.5, alpha = 0.75) +
  geom_point(size = 0.1, shape = 4) +
  geom_vline(xintercept = 0) +
  labs(x = "Participant-level adjustment", y = "Participant", colour = "Group") +
  theme_custom() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    axis.text.x = element_text(size = 9),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

#### Marginal effects {.tabset .tab-pills}

##### By PTHN

```{r emmeans_pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
nd <- expand_grid(
  pthn = seq(
    min(responses_coded$pthn, na.rm = TRUE),
    max(responses_coded$pthn, na.rm = TRUE),
    by = 0.1
  ),
  onset = unique(responses_coded$onset),
  overlap_stress = unique(responses_coded$overlap_stress),
  vowel_ratio = c(-1, 1),
  consonant_ratio = c(-1, 1)
) %>% 
  mutate(frequency = 0)

m <- add_fitted_draws(nd, fit_responses, n = 20, re_formula = NA) %>% 
  mutate_at(vars(ends_with("_ratio")), function(x) paste0(x, " SD")) %>% 
  mutate(
    overlap_stress = paste0("Stress: ", overlap_stress),
    onset = paste0("Onset: ", onset)
  )

ggplot(m, aes(pthn, .value, 
              colour = interaction(consonant_ratio, vowel_ratio, sep = "/"),
              fill = interaction(consonant_ratio, vowel_ratio, sep = "/"))) +
  facet_wrap(~onset) +
  # stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Phonological neighbourhood density\n(higher frequency neighbours)",
       y = "P(Correct)", colour = "Consonant/Vowel similarity",
       fill = "Consonant similarity/Vowel similarity") +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent) +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_pthn.png"))

##### By consonant similarity

```{r emmeans_consonant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
nd <- expand_grid(
  pthn = c(-1, 1),
  onset = unique(responses_coded$onset),
  overlap_stress = unique(responses_coded$overlap_stress),
  vowel_ratio = c(-1, 1),
  consonant_ratio = seq(
    min(responses_coded$consonant_ratio, na.rm = TRUE),
    max(responses_coded$consonant_ratio, na.rm = TRUE),
    by = 0.1
  )
) %>% 
  mutate(frequency = 0)

m <- add_fitted_draws(nd, fit_responses, n = 20, re_formula = NA) %>% 
  mutate_at(vars(vowel_ratio, pthn), function(x) paste0(x, " SD")) %>% 
  mutate(
    overlap_stress = paste0("Stress: ", overlap_stress),
    onset = paste0("Onset: ", onset)
  )

ggplot(m, aes(consonant_ratio, .value, 
              colour = interaction(pthn, vowel_ratio, sep = "/"),
              fill = interaction(pthn, vowel_ratio, sep = "/"))) +
  facet_wrap(~onset) +
  # stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Consonant similarity (SD)",
       y = "P(Correct)", colour = "PTHN/Vowel similarity",
       fill = "PTHN/Vowel similarity") +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent) +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_consonant.png"))

##### By vowel similarity

```{r emmeans_vowel, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
nd <- expand_grid(
  pthn = c(-1, 1),
  onset = unique(responses_coded$onset),
  overlap_stress = unique(responses_coded$overlap_stress),
  vowel_ratio = seq(
    min(responses_coded$vowel_ratio, na.rm = TRUE),
    max(responses_coded$vowel_ratio, na.rm = TRUE),
    by = 0.1
  ),
  consonant_ratio = c(-1, 1),
) %>% 
  mutate(frequency = 0)

m <- add_fitted_draws(nd, fit_responses, n = 20, re_formula = NA) %>% 
  mutate_at(vars(consonant_ratio, pthn), function(x) paste0(x, " SD")) %>% 
  mutate(
    overlap_stress = paste0("Stress: ", overlap_stress),
    onset = paste0("Onset: ", onset)
  )

ggplot(m, aes(vowel_ratio, .value, 
              colour = interaction(pthn, consonant_ratio, sep = "/"),
              fill = interaction(pthn, consonant_ratio, sep = "/"))) +
  facet_wrap(~onset) +
  # stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Vowel similarity (SD)",
       y = "P(Correct)", colour = "PTHN/Consonant similarity",
       fill = "PTHN/Consonant similarity") +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent) +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_vowel.png"))
```
##### {-}

@@

```{r jtrace_all_plot, echo=FALSE, warning=FALSE}
ggplot(jtrace, aes(x = activation, y = pct_participant)) +
  geom_smooth(colour = wes_palettes$Darjeeling1[1],
              fill = wes_palettes$Darjeeling1[1],
              alpha = 0.5) +
  geom_point(shape = 1, stroke = 1, alpha = 0.5) +
  labs(
    x = "jTRACE activation value for the word",
    y = "Participants who responded with the word"
  ) +
  scale_y_continuous(labels = scales::percent) +
  theme_custom() +
  theme(
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "trace_average.png"))

@@

# plot by word
jtrace %>% 
  mutate(input_language = paste0(input, " (", language, ")")) %>% 
  ggplot(aes(x = activation, y = pct_participant)) +
  facet_wrap(~input_language) +
  geom_smooth(colour = wes_palettes$Darjeeling1[1],
              fill = wes_palettes$Darjeeling1[1],
              alpha = 0.5) +
  geom_point(shape = 1, stroke = 1, alpha = 0.5) +
  labs(
    x = "jTRACE activation value for the word",
    y = "% participants who responded with the word",
    title = "jTRACE activation against % participants who gave word as response"
  ) +
  theme_custom() +
  theme(
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
